\bf Drift Removal for Time Series Data Using Quantile Trend Filtering

### 2018-12-05 Manuscript/simulation_notes.tex
peak figures and extended BIC function

\includegraphics[width=\linewidth]{Figures/mixednorm_mse.png}
\bibliographystyle{asa}
\bibliography{detrendify}

\end{document}

>>>>

\includegraphics[width=\linewidth]{Figures/mixednorm_mse.png}

\section{Peaks Simulation}
We use another simulation design based on the applied problem we aim to solve. We assume that the measured data can be represented by 
\begin{equation}
Y(t) = s(t) + b(t) + \epsilon
\end{equation} 
where $s(t)$ is the true signal at time $t$, $b(t)$ is the drift component that varies smoothly over time and $\epsilon \sim N(0, \sigma^2)$ is an error component. We assume $t$ is a uniformly spaced sequence between 0 and 1. We generate $b(t)$ using a cubic natural spline basis function with degrees of freedom sampled from 2 to 10 with equal probability, and coefficients drawn from a normal distribution with mean and variance equal to 1. The true signal function is assumed to be zero with Gaussian peaks. The number of peaks is sampled from 5 to 15 with equal probability with centers uniformly distributed between 0.1 and 0.9 and bandwidths uniformly distributed between $2/n$ and $2/n + .01$. One hundred datasets were generated for $n=500$ and $n=1000$.

\begin{figure}
	\caption{Example of simulated peaks, baseline, and observed measurements.}
	\includegraphics[width = \linewidth]{Figures/ex_peaks.png}
\end{figure}

We compare the methods ability to estimate the baseline using a low quantile, $\tau \in \{0.05, 0.1\}$ and calculate the MSE using the simulated baseline value as the standard. The npqw method performs significantly worse than the other methods and is not included in the figures.

\begin{figure}[h!]
	\caption{MSEs compared to the simulated baseline function.}
	\includegraphics[width = \linewidth]{Figures/peaks_mse.png}
\end{figure}

\begin{figure}[h!]
	\caption{Example baseline fit.}
	\includegraphics[width = \linewidth]{Figures/ex_baseline.png}
\end{figure}

\pagebreak

\bibliographystyle{asa}
\bibliography{detrendify}
\end{document}
